Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-17 thesis/thesis.tex
thesis: Review Acknowledgements

>>>>

I would like to thank my thesis advisor Dr. César Augusto Guzmán Álvarez.
He has guided me through the process of writing this work and has reviewed
the whole work suggesting me improvements.

I would also like to acknowledge my father who always gives me its advices and
helps me by giving me its priceless point of view. I would also like to thank
my mother and girlfriend, who have supported me through the entire process
of making and writing this project.

Finally, I would like to mention the acknowledgments that the developers
of the main tools used in this project politely indicate on their web pages.
